\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-21 Manuscript/reply.tex

We extend our gratitude to the Editor and Associate Editor for 
granting us the opportunity to revise this manuscript. We also want to
express our appreciation to the reviewer for their valuable comments.

The manuscript has been revised accordingly with the most notable change being 
the addition of new data in both the GLMM and rank comparison sections in an
attempt to expand the scope of the analysis and derive beter insights.

@@

This outcome is not unexpected, as athletes competing in longer sprint
events, such as the 200-meter dash, may not prioritize reaction time
as highly as those specializing in shorter sprints like the 100-meter
dash. While it is common for amateur and collegiate athletes to
compete across multiple sprint distances, elite athletes at the World
Championship level may not exhibit equally strong performances in all
sprint events. Our study aims to evaluate the probability of observing
extreme reaction times, particularly in the context of the 0.1-second
threshold. Including data from events with systematically slower
reaction times would artificially inflate the extremity of a
0.1-second reaction time, potentially biasing our conclusions.

In the revision, we have added explanation about why 100-meter dash
data for both men and wemen were included, while 200-meter dash data
were not included in our analysis in Section~???, paragraph~???.
The subsequent analyses in the manuscript have been updated with the
expanded dataset that included both men and women's 100-meter dash
data; see updated results in Sections~???.

@@

The heat effect measures the speed-level of the heat.  We added some additional
explanations in the first paragraph of section 3.2 to make it clear what the
venue and heat effect refer to. We did not want to call it a "race effect" as we
were worried that may be interpreted to mean the race of the athlete.  We did
not think it would be informative to  add and effect for individual runner's
average ability as many of observations in the data come from runners
\jy{It's the number of runners with 1 data point that determines how
  hard the athlete effect can be estimated. How many runers had only 1
  data point?}
with very few (1-3) data points, so taking an average of such a small sample may
not be informative, especially if there are outliers or an athlete had a bad
start.

@@

Thank you for the positive feedback. We expanded both the rank
comparison and the GLMM sections with additional data to strengthen our
analysis. These enhancements support our findings of an anomaly in
2022 and highlight that the 0.1-second reaction time threshold lacks a
foundation in formal statistical evidence.

\subsection*{Reviewer2}

@@

@@

The nomenclature for the greek variables in Table 2 are defined in the GLMM
subsection of the methods section (3.2)

@@

Yes, the comments about the difficulty of data gathering are meant to demostrate
that we worked hard to find as much data as we could and as a note to World
Athletics (track and field governing body) that they need to do a better job
at data standardization.  Currently the races on their website do not include
reaction times, which meant that we had to look in alternative places to perform
the analysis that we did.  The data we found from national level meets in 2022
was difficult to come by as it required searching for every country's championship
results individually and when we did find it, it was often in the native language
making it harder to understand and interpret.

@@

We included this plot to show the venue effect for each year and to visually
demonstrate how 2022 compares to other years.  We added additional comments
about the probability of observing an extreme venue effect to provide
quantitative data supporting our argument.

>>>>

We extend our gratitude to the Editor and Associate Editor for 
granting us the opportunity to revise this manuscript. We also want to
express our appreciation to the reviewers for their valuable comments.

The manuscript has been revised accordingly with the most notable change being 
the addition of new data in both the GLMM and rank comparison sections in an
attempt to expand the scope of the analysis and derive better insights.

@@

This difference in reaction times is not unexpected, however, as athletes 
competing in longer sprint
events, such as the 200-meter dash, may not prioritize reaction time
as highly as those specializing in shorter sprints like the 100-meter
dash. While it is common for amateur and collegiate athletes to
compete across multiple sprint distances, elite athletes at the World
Championship level may not exhibit equally strong performances in all
sprint events. Our study aims to evaluate the probability of observing
extreme reaction times, particularly in the context of the 0.1-second
threshold. Including data from events with systematically slower
reaction times would artificially inflate the extremity of a
0.1-second reaction time, potentially biasing our conclusions.

In the revision, we have added explanation about why 100-meter dash
data for both men and wemen were included, while 200-meter dash data
were not included in our analysis in Section~???, paragraph~???.
The subsequent analyses in the manuscript have been updated with the
expanded dataset that included both men and women's 100-meter dash
data; see updated results in Sections~???.
\eds{let's revisit this again after objective 2 analyses are set}

@@

We apologize for the confusion. The heat effect actually measures the speed-level 
of the heat, not the type of heat.  We added some additional
explanations in the first paragraph of section 3.2 to make it clear what the
venue and heat effect refer to. We did not want to call it a ``race effect" as we
were worried that may be interpreted to mean the race of the athlete.  We did
not think it would be informative to  add and effect for individual runner's
average ability as many of observations in the data come from runners
\jy{It's the number of runners with 1 data point that determines how
  hard the athlete effect can be estimated. How many runners had only 1
  data point?}
with very few (1-3) data points, so taking an average of such a small sample may
not be informative, especially if there are outliers or an athlete had a bad
start.
\eds{let's revisit this again after objective 2 analyses are set}

@@

Thank you for the positive feedback. We expanded both the rank
comparison and the GLMM sections with additional data to strengthen our
analysis. These enhancements support our findings of an anomaly in
2022 and highlight that the 0.1-second reaction time threshold lacks a
foundation in formal statistical evidence.
\eds{let's revisit this again after objective 2 analyses are set}

\subsection*{To Reviewer 2}

@@

Please see our second response to Reviewer 1 for additional 
comments relating to longer sprint events (200-meter or longer), 
and why these were not also included in our analyses.

@@

The nomenclature for the greek variables in Table 2 are defined in the GLMM
subsection of the methods section (3.2).
\eds{let's revisit this again after objective 2 analyses are set}

@@

Yes, the comments about the difficulty of data gathering are meant to demonstrate
that we worked hard to find as much data as we could and, as a note to World
Athletics (track and field governing body), that they need to do a better job
at data standardization.  Currently the races on their website do not include
reaction times, which meant that we had to look in alternative places to perform
the analyses that we did.  The data we found from national level meets in 2022
was difficult to come by as it required searching for every country's championship
results individually and when we did find it, it was often in the native language
making it harder to understand and interpret.

@@

We included this plot to show the venue effect for each year and to visually
demonstrate how 2022 compares to other years.  We added additional comments
about the probability of observing an extreme venue effect to provide
quantitative data supporting our argument.
\eds{let's revisit this again after objective 2 analyses are set}
